%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../../main"
%%% End:

% pre set seeds
% - extract from camera
% - extract all from server

The first part of the system we would like to review is the encryption
of the video stream~\cite[sec. 3]{8}. We will look at this process i
two steps; the video stream from camera to server and the transfer
from server to storage.

\subsubsection{Proposed solution}

As explained in the report, the current system distributes a preset
seeds to cameras upon setup~\cite[sec. 3.2.4]{8}. Each camera gets an
identical seed to avoid collision.

The report states, ``physical attacks on the camera are not
considered''~\cite[p. 2]{8}, but we would still like consider how the
physical equipment could be tampered with. More specifically, if the
preset encryption seed could be extracted.

If the preset seed of each camera could be extracted and used by an
passive or active adversary. In the case of a passive adversary, all
transmissions could be intercepted. In latter case, an active
adversary could perform Man in the Middle (MITM) attacks, as he or she
could also forge new transmissions.

Having pointed this out, there are still risk with such preset seeds
without requiring physical tampering with the equipment. Another
option is to compromise the server itself. As the report states, the
server has the unique seeds to all cameras stored, so it can decrypt
their data~\cite[p. 8]{8}. If the server was compromised, an adversary
could do passive and active attacks on the video streams of \emph{all}
cameras. Again, it does not only compromise the confidentiality of the
data, but the integrity. For instance, fake evidence material could be
planted etc.


\subsubsection{Alternative}

The report discusses if the video streams should be stored directly,
assuming the encryption is strong enough, or if the data should be
re-encrypted. Having discussed the effects of compromised hardware or
server in the previous section, we would like to propose an
alternative solution making said attack impossible.

If the server is compromised it would not matter if the data is stored
directly or re-encrypted, because the data could be respectively
decrypted or intercepted before re-encryption.

% tls encryption instead puzzle
% - stardard, tried and true

% public-key end-to-end encryption (with tls in transit)
% - hardware encryption?

% http://www.cebit.de/product/video-surveillance-end-to-end-encryption/2000024/Y971710
% http://www.accellence.de/en/produkte/vimacc.html

% http://www.buykorea.org/product-details/video-surveillance-system-end-to-end-encryption-cc-camera-ip-camera--3021098.html

TODO marcus
